As Gregory Maxwell awoke from his alarm, he could feel the tingling sensation leave his limbs as probes left their magnetic anchor points on his shoulders and ankles.
The man’s rather defined arms propped him up as he tried to wake himself up.
Moving his legs to the side of the bed, he rubbed his eyes in an attempt to get rid of the yellow rheum that had seemed to build up in them throughout the night.

After he finished, his eyes were blinded for a few moments as monochrome green light was sprayed across his face from the monitor that sat on the bed’s night stand.
Long gone where the days of colorful displays, especially crafted icons, and graphical interfaces in any form of the word.
They had simply become unnecessary as it had been found that humans slowed down the processes of almost all software, and therefore they were removed from the equation in most cases.
Given that the system that sat on Greg’s side was practically ubiquitous among the people around him, it simply printed text to the screen, reading:
\begin{center}
\verb|DREAM DATA UPLOADING|\\
\verb|CREDIT GAIN= 0.02%|\\
\verb|AVAILABLE CREDITS= 65.62%|
\end{center}
The man yawned, his throat dry from the lack of moisture in the room.
It decreased the efficiency of the software that gathered data on his dreams and fed him advertisements in the interim periods between REM cycles.
Gregory stood, his joints popping softly-an old side effect of the nano gel injections they used to preserve cartilage during longer sleep cycles.
The floor beneath his bare feet adjusted the temperature automatically, deciding he was $.02$ degrees cooler than normal.
Rolling his eyes, he ignored it.

Looking through the floor to the ceiling window at the foot of his bed, he could see that the rain from when he went to sleep
had not left him, still shooting down the long windows, collecting somewhere in the ground streets, far from what he could see at his present vantage point.
The room was minimal and angular, all sharp edges and cold metal.
Sleek panels decorated the edges of the floor, shifting colors throughout the day, and the bed, low to the ground, looked far more like an abstract exhibit than anything made for sleeping in.
Pale blue light filtered in through the window, casting watery reflections that danced across the smooth floor.

Gregory’s visual exploration of the room abruptly ended as with another flash of light, the monitor cleared all previous information but the top line.
\begin{center}
\verb|DREAM DATA UPLOAD COMPLETE|
\end{center}
After the standard four seconds passed, the screen cleared once more, shutting off after the screen was completely cleared.
As the system shut off, the room’s door in front of him was unlocked with an electronic click.
It had been determined that many people where not interested in allowing the dream data to completely upload if they did
not have an incentive to do so, so the powers that be decided the best  incentive was to simply lock their citizens in their bedrooms until all the data was sent to the cloud network.

he gathered data was taken and compiled for two broad reasons: the health of the individual, and to keep tabs on the thoughts and possible motives of the individual.
In terms of the health of the individual, the dream data tracked the oxygen levels and respiration rate to ensure proper rest, as well as muscular relaxation.

It was well known that the physical health of the individual was paramount in the eyes of the government, but that did not
seem to stop them from also keeping tabs on the thoughts and dreams experienced by the individual as well.
The publicly given reasoning for this was to ensure that citizens where not experiencing distress or anxiety, and to ensure that they were not a victim of misinformation.
However, this was not the sentiment held by the general population, who had theories ranging from simple advertisement placement data to
a more complex form of data that would allow for the creation of a more accurate model of the human mind, one that could be molded to the whims of those who held the power.

Now freed from the rom by the unlocked door, Gregory Maxwell stepped out of the bedroom and into the main area of his apartment.
In this area was a small living area with an L-shaped couch with a coffee table in the middle, and a wall-mounted television in front.
to the right of anyone sitting at the table was another floor to ceiling window, holding a simular view to the one in his bedroom.
To the man's right, and the left of the couch was the food preparation area, as well as the controls for the apartment.

As Maxwell made his way to the food preparation area, he could hear the female voice of his AI personal assistant, Sarah, speaking to him.
\("\)Good morning sir, how may I be of assistance today?\("\).
Greg rubbed his eyes again, looking around aimlessly before replying to his assistant \quotes{Surprise me, Sarah, but make sure it’s caffeinated,} he replied roughly, his voice still hoarse from the night before.
His voice dripped with sarcasm, still carrying the usual dose of snark that only years of the same, dull routine could force upon someone.
Pausing as more of a retaliation of her own than the need to process what the man said, Sarah soon replied with a glass of dirt-brown liquid \quotes{Caffeine enriched water it is, sir.
May I remind you that you need to leave this location in 5.8 minutes to ensure an efficient arrival time to the train station?}
the AI informed him. \quotes{Yeah, yeah, I know.} Greg rolled his eyes, these damn robots, always so apt and efficient.
\quotes{Sir} Sarah chimed in. \quotes{If you are going to criticize me, I recommend that you do it where I cannot see it.}
Greg’s eyes spun once more as he grabbed the drink and his book bag before opening the door \quotes{Thank you, Sarah.}
The door closed behind him before he could hear the too-happy voice chirp back a reply behind the sleek metal of his apartment door.

\dinkus
